Extreme Value Chapter 3

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 3 for parameter estimation is ready and in the word document.

# Figure 2
First let's see the true thetas, which because of small numbers we are visualizing in log scale for the second panel:

```{r fig.width=5, fig.height=2.5}
# thetas %>% 
#   ggplot(., aes(x = thresh_tests, y = theta)) +
#   geom_point(size = 4, shape = 18, color = theta_color) +
#   labs(x = "Long-distance level", y = "Theta") +
#   theme_bw() -> a

@@

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") -> b

@@

@@

```{r fig.width=7, fig.height=4}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "bottom") -> a

>>>>

# Figure 2

```{r eval=FALSE, fig.width=5, fig.height=2.5}
# thetas %>% 
#   ggplot(., aes(x = thresh_tests, y = theta)) +
#   geom_point(size = 4, shape = 18, color = theta_color) +
#   labs(x = "Long-distance level", y = "Theta") +
#   theme_bw() -> a

@@

```{r fig.width=6, fig.height=4}

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "right") -> b

@@

GP_mles %>% 
    mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> c

abplot <- plot_grid(a, b + theme(legend.position = "none"), c, nrow = 3, labels = "AUTO", label_size = 8)

plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.2))
ggsave("Ch3_samplesize/Figures/Figure2.png")

@@

```{r fig.width=4, fig.height=2.5}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "bottom") -> a
